---
output: github_document
---
  
## Campsisverse

The official R package manager of the Campsis suite.

### Install Campsisverse

Install the Campsisverse package with the following command:

```{r eval=FALSE}
remotes::install_github("Calvagone/campsisverse")
```
  
### Restore the Campsis suite

Restoring the Campsis suite into your R distribution is easy. Just run the following command:

```{r eval=FALSE}
campsisverse::restore(version="24-12-01")
```

By executing this command, the whole Campsis suite is installed in your R distribution based on the `renv.lock` file dated on the 1st of December 2024, i.e., the latest Campsis snapshot available at the time of writing. Thanks to this file, the Campsis suite is restored with the exact versions of the packages that were used to create the snapshot.  

Specific versions of the Campsis suite can be restored by specifying the `version` argument. This importantly ensures the reproducibility of your simulation scripts over time.  

In case you want the Campsis dependencies (e.g. `dplyr`, `ggplot`, etc.) to be installed without specific versions, use the `no_deps` argument. When `no_deps` is TRUE, only the Campsis packages are installed with the versions specified in the lock file. This argument may be useful if your R distribution points to a snapshot repository and you must stick to a snapshot date.

```{r eval=FALSE}
campsisverse::restore(version="24-12-01", no_deps=TRUE)
```

Please be aware that setting `no_deps` to TRUE may cause unexpected behavior of some Campsis packages. In any case, we recommend using our qualification package to validate the correct functioning of Campsis. Please visit the [Campsisqual repository](https://github.com/Calvagone/campsisqual) for more information.

### Running the Campsis suite in a sandbox with renv

The Campsis suite can be run in a sandbox environment using the `use` function. This function is useful when you want to run the Campsis suite in a temporary environment without affecting your current R distribution. 

```{r eval=FALSE}
campsisverse::use(version="24-12-01")
```



